Forecasting Influenza Hospitalizations Using a Bayesian Hierarchical Nonlinear Model with Discrepancy

### 2025-12-01 response_round1.tex

        \[
         \widetilde{H}_{s,w + i}^{(k)} = \alpha_{0s}^{(k)} + 
                                          \alpha_{1s}^{(k)} 
                                          (\widetilde{ILI}_{s,w +i}^{(k)} \times P) + 
                                          \alpha_{2s}^{(k)} 
                                          (\widetilde{ILI}_{s,w +i}^{(k)} \times P)^2 + 
                                          \phi^{(k)} \widetilde{H}_{s,w + i - 1}^{(k)} + 
                                          \epsilon_{s,w + i}^{(k)}
        \]
        \emph{where $k \in \{1, ..., K\}$. The hospitalization draws were then combined into
        $\{H^{(k)}_{s,w + i}\}^K = (\widetilde{H}_{s,w + i}^{(1)}, ..., \widetilde{H}_{s,w + i}^{(K)})$,
        from which
        the probabilistic hospitalization forecast was estimated. In practice we set
        $K = 50,000$, and forecasts were obtained for weeks $i \in \{1, 2, 3, 4\}$.
        \\~\\
        \indent Occasionally $\{H^{(k)}_{s,w + i}\}^K$ included a small number of negative 
        values,
        which do not make sense when the distribution is meant to forecast
        hospitalizations, a nonnegative number. We attempted to alleviate this problem
        by modeling log-hospitalizations or by assuming hospitalizations followed a
        distribution truncated at 0, but these models led to poorer forecasts
        and issues drawing from the posterior distribution.
        For the forecast competition analysis in 
        section 5, all negative values of $\{H^{(k)}_{s,w + i}\}^K$ 
        were 
        set to 0 to reflect realistic values of hospitalizations and comply with the 
        FluSight forecasting rules.}
        \\~\\
        \emph{
        \indent In the two-stage scheme, the posterior distribution of 
        model (1) parameters was not directly influenced by the 
        hospitalization data and the posterior distribution of model 
        (6) parameters was not directly influenced by model 
        (1) parameters. Hence there was limited feedback between the
        two components, but propagation of uncertainty in ILI forecasts was still 
        permitted in the estimating of hospitalization forecasts.
        This two-stage modeling is remeniscent of the Bayesian cut 
        described in \cite{plummer2015cuts} and \cite{nott2023bayesian}. Cutting a model
        into two component models or ``modules`` may be justified for several reasons
        including to reduce time to fit the model, avoiding mixing issues of posterior
        sampling distributions, improving predictive performance or to prevent
        model misspecification in one model to influence the other 
        \cite[]{nott2023bayesian, jacob2020unbiased, jacob2017better, 
        lee2017rigorous, plummer2015cuts}. A drawback
        from cutting a model is potential loss of useful information. 
        In our current 
        application for example, the ILI model parameters receive no potentially 
        useful information from hospiatlization data.
        \\~\\
        \indent The decision to cut the forecast model into two component models
        was made for three major reasons.
        When fitting the fully Bayesian joint model, the time to fit a single model 
        using
        MCMC sampling and
        obtain forecasts was sometimes many hours whereas fitting the two models
        separately took a fraction of the time. When assessing convergence of model
        parameters, it was rare that posterior sampling chains for the joint model
        showed convergence even after 55,000 iterations, whereas the component model 
        fits gave no signs which raised concern for convergence. And most importantly,
        the forecasts from the component models generally outperformed those of the 
        joint model in terms of minimizing proper scoring rules.}
        \\~\\
  \end{quote}

In conclusion, I do think that the authors have done a good job of analysis and 
simulation based demonstrations of the results. These can be further improved 
by including some better measures of assessing prediction/forecasting accuracy, 
e.g. the CRPS (Continuous Ranked Probability Score), see for example Chapter 6 
of the book
``Bayesian modeling of spatio-temporal data with R`` by Sahu 
(Chapman and Hall, 2022). 
\\~\\
\emph{In the simulation study in section 4 of the first version of this paper, 
scoring was
done using the CRPS, but in the FluSight analysis in section 5 scoring was done
using the WIS because the available forecasts are not amenable to being scored
the with the CRPS. A recommendation from one of the reviewers was to simplify 
by choosing one or the other scores, and we chose the WIS. To respond to this 
point, however, we modified the first paragraph on page 17. The paragraph is 
below and the added statements are bolded.
}

\begin{quote}
\emph{
Model comparison was done by calculating a proper scoring rule for each 
forecast.
Proper scoring rules are the 
current standard for comparing performance between probabilistic forecasts 
and selecting the best forecasts according to the notion of maximizing 
sharpness subject to (auto-)calibration 
\cite[]{gneiting2007probabilistic, tsyplakov2013evaluation}. Proper scoring 
rules are commonly used in forecast comparison, and they are designed such 
that a 
forecaster is incentivized to be honest in the reporting of their forecasts 
\cite[]{gneiting2007strictly, gneiting2014probabilistic}.
\textbf{Commonly used proper scoring rules for continuous distribution forecasts
include the log score and the continuously
ranked probability score (CRPS).} 
The proper scoring rule primarily used in the FluSight competition and the 
COVID-19 Forecast Hub, and which is used in this simulation study,
is the negatively oriented
(smaller is better)
weighted interval score (WIS)
\cite[]{mathis2024evaluation, bracher2021evaluating}.
The WIS is used for scoring quantile or interval 
forecasts \textbf{--the forecast format used in both FluSight and the 
COVID-19 Forecast Hub--}
or forecasts made up of predicitive intervals of several nominal 
levels
\cite[]{gneiting2007strictly, gneiting2014probabilistic, bracher2021evaluating}. 
The WIS is 
defined in (8) where $Q$ is a forecast represented by all 
included quantiles, $B$ is the number of intervals,  $y^*$ is the observed 
value targeted by the forecast, $w_0 = 1/2$ and $w_b = \alpha_b / 2$ are 
weights for each interval, and $\alpha_b$ is the nominal level of the $b^{th}$ 
interval where $b \in \{1, ..., B\}$. 
$IS_{\alpha}$ is the interval score (IS), a proper scoring rule for a 
single interval, defined in (9). Here 
$\vmathbb{1}\{\cdot\}$ is the indicator function.
\textbf{We note that as the number of forecast intervals $B$ increases, the WIS becomes 
arbitrarily close to
the CRPS. Thus, forecast scores under the CRPS and the WIS should be similar
\cite[]{bracher2021evaluating}.}}
\end{quote}
